---
title: "Class 12: Structural Bioinformatics:Drug Discovery"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents


```{r}
library(bio3d)
```

#here, lets first download a target(i.e a protein receptor) structure from the main PDB databaes. we will pick up PDB 1D "1hsg"
```{r}
pdb.code<-"1hsg"
file.name<-get.pdb(pdb.code)
```

#extract the proteiin only segment of this PDB entry and write out a new PDB formation file. We will also do the same for the bound ligand 

```{r}
hiv<-read.pdb(file.name)
hiv
```

#protein extraction first 

```{r}
prot<-trim.pdb(hiv,"protein")
prot
```

```{r}
prot.file=name<-paste(pdb.code,"_protein.pdb",sep="")
write.pdb(prot,file= prot.file)
```

#do the same for the ligand
```{r}
lig<-trim.pdb(hiv,"ligand")
lig


```

```{r}
lig.file=name<-paste(pdb.code,"_ligand.pdb",sep="")
write.pdb(lig,file= lig.file)
```

```{r}
lig
```

## convert our docking results for viewing in VMD 
```{r}
library(bio3d)
res <- read.pdb("all.pdbqt", multi=TRUE)
write.pdb(res, "results.pdb")
res
```


```{r}
res <- read.pdb("all.pdbqt", multi=TRUE) 
ori <- read.pdb("ligand.pdbqt")
rmsd(ori, res)
```




